---
title: '6060 Practice: RMarkdown'
author: "Janie Vu"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
  html_document:
    toc_depth: '3'
---

<center>
# 6060 Practice: RMarkdown
*Janie Vu*
</center>

# **Relations among variables for women**
Below are the correlations among the variables for women.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(apaTables)

#Load data 
analytic.data.female        <- read_csv("quiz2_analytic_data_female.csv")

#Correlations
psych::pairs.panels(as.data.frame(analytic.data.female),lm=FALSE)

```

\pagebreak

# **Distributions**

## **Distribution of negative affect scores**

Below we can see the distribution of negative affect scores is skewed.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Load data 
analytic.data.female        <- read_csv("quiz2_analytic_data_female.csv")

my.hist <- ggplot(analytic.data.female,aes(neg_affect))
my.hist <- my.hist + geom_histogram(aes(y= ..count..), binwidth= .1, fill="gray30", color="gray30")
my.hist <- my.hist + labs(x="Negative Affect", y="Frequency")
my.hist <- my.hist + theme_classic(14)
my.hist <- my.hist + theme(axis.line.x = element_line(colour = 'gray30', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'gray30', size=0.5, linetype='solid'))
my.hist <- my.hist + scale_x_continuous( breaks = seq(0,3,by=1) )
my.hist <- my.hist + scale_y_continuous( breaks = seq(0,1200,by=300), expand=c(0,0) )
print(my.hist)  
```

\pagebreak

## **Neuroticism Distribution**

Below we can see the distribution of neuroticism scores is relatively normal.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Load data 
my.hist <- ggplot(analytic.data.female,aes(Neuroticism))
my.hist <- my.hist + geom_histogram(aes(y= ..count..), binwidth= .75, fill="gray30", color="gray30")
my.hist <- my.hist + labs(x="Neuroticism", y="Frequency")
my.hist <- my.hist + theme_classic(14)
my.hist <- my.hist + theme(axis.line.x = element_line(colour = 'gray30', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'gray30', size=0.5, linetype='solid'))
my.hist <- my.hist + coord_cartesian(xlim=c(0, 25), ylim=c(0, 1200))
my.hist <- my.hist + scale_x_continuous( breaks = seq(0,25,by=5) )
my.hist <- my.hist + scale_y_continuous( breaks = seq(0,1200,by=300), expand=c(0,0) )

print(my.hist)
```

\pagebreak

# **Relations among variables**

## **Scatter plot for Negative Affect and Neuroticism**

Below we can see the correlation between negative affect and neuroticism with a regression line.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.plot <- qplot(neg_affect, Neuroticism, data=analytic.data.female)
my.plot <- my.plot + theme_classic(14)
my.plot <- my.plot + theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
                           axis.line.y = element_line(colour = 'black', size=0.5, linetype = 'solid'))
my.plot <- my.plot + labs(x="Negative Affect", y="Neuroticism")
my.plot <- my.plot + coord_cartesian(xlim=c(0,3), ylim=c(0,25))
my.plot <- my.plot + geom_smooth(method = "lm", se = FALSE, color="black")

print(my.plot)
```


